Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-03-06 text/old_spring2024/front_end_v2.qmd
working through front end. again.

>>>>

Institutional theory defines the organizational field as "those organizations that, in the aggregate, constitute a recognized area of institutional life: key suppliers, resource and product consumers, regulatory agencies, and other organizations that produce similar services and products" [@RN527, p. 143].
